DNSKEY Management

### 2012-12-05 paper/paper.tex
coherent dotting for domains/zones.

By signing the keys of the TLD's, the root will put its trust into their keys, and any keys the TLD's have signed, resulting in a trust hierarchy illustrated in fig.~\ref{fig:trust-chain}. This way, a resolver querying the LACAL's DNS server for \verb|lacal.epfl.ch| will be able to verify the received query answer against the known root-authority in the following way:

\begin{enumerate}
\item Verify the reply's authenticity using \verb|lacal.epfl.ch|'s public key, obtained from \verb|epfl.ch|'s DNS server ;
\item Verify the query -- containing \verb|lacal.epfl.ch|'s public key -- returned by \verb|epfl.ch| with its public key, retrieved from the \verb|.ch| DNS server;
\item Again, verify \verb|.ch|'s responses by getting its public key from the root domain.
\item Finally, the root domain's responses can be verified with its already known public key.
\end{enumerate}

@@

\section{Operations\wbjp}
This section covers the issues and quirks related to the management of DNSSEC.
\subsection{3Rs}
%% Talk about EPP or push burden to Case-Study
Regarding the management of the Internet namespace, three entities can generally be considered, namely:

\begin{itemize}
\item \textbf{R}egistries;
\item \textbf{R}egistrants;
\item \textbf{R}egistrars.
\end{itemize}

The registries are the entities serving the records for a zone. For example, Switch is the registry for the \verb|ch.| zone. Registrants, on their side, are the entities willing to obtain a certain domain: the registrant of \verb|epfl.ch| is the school in itself (its IT-department to be precise \footnote{As a \emph{whois} query on the epfl.ch domain will show you.}), for example.

@@

Registrants are also free to play the registry and registrar roles for their own sub-domains: groups, laboratories and associations within EPFL may apply for an \verb|epfl.ch| sub-domain, like the LACAL and it's \verb|lacal.epfl.ch| subdomain, for example.

@@

Signing new zones will have different administrative implications depending on whether the parent zone is in the same administrative entity or not: e.g., \verb|www.epfl.ch| is managed by the same entity as \verb|epfl.ch|, so signing the \verb|www| sub-domain will imply a different (and very likely easier) procedure than signing \verb|epfl.ae|, EPFL's domain for its middle-east campus.

@@

\subsubsection{Multiple administrative domain}
DNSSEC's true challenges arise when we begin to consider several administrative entities (the three R's, mainly). As stated earlier, once the \verb|epfl.ch| zone is signed it is easy for the school to sign \verb|www.epfl.ch|. However, if the domain to be signed was \verb|epfl.ch| or \verb|epfl.ae|, the school would have to deal with the entity or entities managing the TLD's (\verb|ch.| managed by Switch or \verb|ae.|\footnote{epfl.ae has been registered at 'Instra Corporation Pty Ltd', a registrar for the ae.}, respectively), which will have they own terms and conditions, which might very well be different among different registrars and TLD's.

While standard DNS can perfectly live with some of the temporary imprecisions generated by non-optimal interactions between the three R's, DNSSEC is far less tolerant to such jitter: typically, if the \verb|epfl.ch| zone updates its keys but Switch fails to reflect this change fast enough in its records, query responses from \verb|epfl.ch|'s DNS servers will appear as illegitimate whereas they perfectly are, and this will last as long as Switch's servers do not reflect the update.

>>>>

By signing the keys of the TLD's, the root will put its trust into their keys, and any keys the TLD's have signed, resulting in a trust hierarchy illustrated in fig.~\ref{fig:trust-chain}. This way, a resolver querying the LACAL's DNS server for \verb|lacal.epfl.ch.| will be able to verify the received query answer against the known root-authority in the following way:

\begin{enumerate}
\item Verify the reply's authenticity using \verb|lacal.epfl.ch.|'s public key, obtained from \verb|epfl.ch.|'s DNS server ;
\item Verify the query -- containing \verb|lacal.epfl.ch.|'s public key -- returned by \verb|epfl.ch.| with its public key, retrieved from the \verb|ch.| DNS server;
\item Again, verify \verb|ch.|'s responses by getting its public key from the root domain.
\item Finally, the root domain's responses can be verified with its already known public key.
\end{enumerate}

@@

\section{Operations\wbjp}
This section covers the issues and quirks related to the management of DNSSEC.
\subsection{3Rs}
%% Talk about EPP or push burden to Case-Study
Regarding the management of the Internet namespace, three entities can generally be considered, namely:
\begin{itemize}
\item \textbf{R}egistries;
\item \textbf{R}egistrants;
\item \textbf{R}egistrars.
\end{itemize}

The registries are the entities serving the records for a zone. For example, Switch is the registry for the \verb|ch.| zone. Registrants, on their side, are the entities willing to obtain a certain domain: the registrant of \verb|epfl.ch.| is the school in itself (its IT-department to be precise \footnote{As a \emph{whois} query on the epfl.ch domain will show you.}), for example.

@@

Registrants are also free to play the registry and registrar roles for their own sub-domains: groups, laboratories and associations within EPFL may apply for an \verb|epfl.ch.| sub-domain, like the LACAL and it's \verb|lacal.epfl.ch.| subdomain, for example.

@@

Signing new zones will have different administrative implications depending on whether the parent zone is in the same administrative entity or not: e.g., \verb|www.epfl.ch.| is managed by the same entity as \verb|epfl.ch.|, so signing the \verb|www| sub-domain will imply a different (and very likely easier) procedure than signing \verb|epfl.ae|, EPFL's domain for its middle-east campus.

@@

\subsubsection{Multiple administrative domain}
DNSSEC's true challenges arise when we begin to consider several administrative entities (the three R's, mainly). As stated earlier, once the \verb|epfl.ch.| zone is signed it is easy for the school to sign \verb|www.epfl.ch.|. However, if the domain to be signed was \verb|epfl.ch.| or \verb|epfl.ae|, the school would have to deal with the entity or entities managing the TLD's (\verb|ch.| managed by Switch or \verb|ae.|\footnote{epfl.ae has been registered at 'Instra Corporation Pty Ltd', a registrar for the ae.}, respectively), which will have they own terms and conditions, which might very well be different among different registrars and TLD's.

While standard DNS can perfectly live with some of the temporary imprecisions generated by non-optimal interactions between the three R's, DNSSEC is far less tolerant to such jitter: typically, if the \verb|epfl.ch.| zone updates its keys but Switch fails to reflect this change fast enough in its records, query responses from \verb|epfl.ch.|'s DNS servers will appear as illegitimate whereas they perfectly are, and this will last as long as Switch's servers do not reflect the update.
